An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-12 paper/paper.tex

%%\usepackage{setspace}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{alltt}
\usepackage{color}
\usepackage{fancyvrb} 
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{url}
%\usepackage[autostyle]{csquotes} 
%\usepackage[toc,page]{appendix}

%\usepackage[top=1in, bottom=1.5in, left=1.5in,right=1.5in]{geometry} % setting the page alignment with this package

@@

\begin{document}
\begin{center}
\thispagestyle{empty}
% TODO install \textsc font
\Large{\textbf{A Major Qualifying Project Report\\ \large{ON}}}\\[0.7cm]
\LARGE{\textsc {\textbf{An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems}}}\\[0.5cm]
\vspace{0.2cm}
\Large{\textbf{\\Submitted to the Faculty of }}
\LARGE{\textbf{\\WORCESTER POLYTECHNIC INSTITUTE\\}}
\vspace{0.5cm}
\Large{\textbf{\\In Partial Fulfillment of the Requirement for the}}
\Large{\textbf{\\Degree of Bachelor of Science}}
\vspace{0.5cm}
\Large{\textbf{\\by}}\\[0.5cm]
\large{\textbf{Dan Bouffard}}\\
\large{\textbf{Marc Green}}\\
\vspace{0.5cm}
\large{\textbf{UNDER THE GUIDANCE OF}}\\
\large{\textbf{Professor G\'abor N. S\'ark\"ozy}}\\
\vspace{1cm}
\large{\textbf{\\May 1, 2014}}\\
\newpage
\end{center}

@@

@@

@@

\chapter{Implementation}
\section{Languages and Tools}
\section{System Design}
\subsection{Overview}
\subsection{}
\subsection{DHT}
\section{Ensuring Backup Safekeeping} \label{sec:challenge}
% This was copied from the explanation of challenge mechanisms in the background info. We will use it down here instead
%A challenge in PeerStore consists of a randomly-generated number followed by a specified range of bytes in the file being backed up. The node holding the peer's data must take the bytes in the specified range, concatenate the random number with that data, take the hash of it, and return the result to the peer. If the correct answer is returned, then the node has passed the challenge. If the node does not respond or gives the wrong answer, the challenge has been failed. By choosing a random subset of bytes and creating a random number to include in the hash, the node cannot calculate the hash ahead of time and only store that; the whole file must be stored in order to be able to successfully complete all possible challenges.

>>>>

%%\usepackage{setspace}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{alltt}
\usepackage{color}
\usepackage{fancyvrb} 
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{url}
\usepackage{verbatim}
%\usepackage[autostyle]{csquotes} 
%\usepackage[toc,page]{appendix}

\usepackage[top=1in, bottom=1.5in, left=1.5in,right=1.5in]{geometry} % setting the page alignment with this package

@@

\begin{document}

\begin{titlepage}
\begin{center}
\thispagestyle{empty}
% TODO maybe nice pic? \includegraphics [width = 0.3\textwidth] {images/wpilogo}\\[0.3cm]
% TODO install \textsc font
\Large{\textbf{A Major Qualifying Project Report\\ \large{ON}}}\\[0.7cm]
\LARGE{\textsc {\textbf{An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems}}}\\[0.5cm]
\vspace{0.2cm}
\Large{\textbf{\\Submitted to the Faculty of }}
\LARGE{\textbf{\\WORCESTER POLYTECHNIC INSTITUTE\\}}
\vspace{0.5cm}
\Large{\textbf{\\In Partial Fulfillment of the Requirement for the}}
\Large{\textbf{\\Degree of Bachelor of Science}}
\vspace{0.5cm}
\Large{\textbf{\\by}}\\[0.5cm]
\large{\textbf{Dan Bouffard}}\\
\large{\textbf{Marc Green}}\\
\vspace{0.5cm}
\large{\textbf{UNDER THE GUIDANCE OF}}\\
\large{\textbf{Professor G\'abor N. S\'ark\"ozy}}\\
\vspace{1cm}
\large{\textbf{\\May 1, 2014}}\\
\end{center}
\end{titlepage}

@@

% TODO citations?

@@

% TODO why do we discuss the different ways to find peers? We only need to talk about predfined hosts

@@

\chapter{BTBackup}

In this chapter, we discuss the design of our Peer to Peer backup system.

\section{Ensuring Backup Safekeeping} \label{sec:challenge}
% This was copied from the explanation of challenge mechanisms in the background info. We will use it down here instead
%A challenge in PeerStore consists of a randomly-generated number followed by a specified range of bytes in the file being backed up. The node holding the peer's data must take the bytes in the specified range, concatenate the random number with that data, take the hash of it, and return the result to the peer. If the correct answer is returned, then the node has passed the challenge. If the node does not respond or gives the wrong answer, the challenge has been failed. By choosing a random subset of bytes and creating a random number to include in the hash, the node cannot calculate the hash ahead of time and only store that; the whole file must be stored in order to be able to successfully complete all possible challenges.

\chapter{Implementation}
\section{Language and Tools}
\section{System Design}
\subsection{Overview}
\subsection{BitTorrent Sync}

Cool new tool, implements bittorrent protocol, but unfortunately closed source. in production ready system, would want to open source (possibility of backdoor, etc)

\subsection{DHT}

Simplification:centralized tracker

\subsection{System Core}

Contrololololololers, etc

\chapter{Methodology}

\chapter{Results}

\chapter{Conclusion}

...

\section{Future Work}
